\chapter{Introduction \\
\small{\textit{-- Team}} 
\index{Chapter!introduction}
\index{introduction}
\label{Chapter::Introduction}}

% Add a section and label it so that we can reference it later
\section{The Team \label{Section::The Team}}

We are a team of three students and below is a biref introduction about us.\\
\textbf{Tanay Shah:}

I am currently pursuing Master's in Computer Science and this is my 2nd Semester. I completed my Bachelors of Computer Engineering in 2020. I worked as a Software Developer for 2 years in an IT firm located in Gujarat, India. I also did freelancing work for a year which included 15 projects. I have good amount of experience in PHP, Java, Python, JavaScript, NodeJS, Laravel Framework, Zend Framework, AWS Management.

\textbf{Chinamy Dali:}

I am currently pursuing a Master's in Computer Science at Stevens Institute of Technology. I have an experience of just over an year in .NET, java spring and nodejs as a full-stack developer; building web-apps and maintaining large scale backends. I am interested in programming languages and compilers, which have been my focus for my graduate studies. I have been built an interpreter for my own language using OCaml and currently pursing Compiler Design course build a X86 architecture targeted compiler for the same language. 

\textbf{Moksha Dave}

I am pursuing my Master's degree with Computer Science as my major. It's my second semester at Stevens and I've been enjoying every part of it. Coming to my bachelor's, I completed my BE in Information Technology from Gujarat Technological University (GTU) during which I studied courses like Data structures, algorithms, computer networks, operating systems, AI, Computer Vision, Data Visualization and a few more. Overall, I am a fast and an enthusiastic learner and a reliable one as well! Something that people wouldn't know about me yet is, I will give in my 110\% once I decide on something.

 \section{Stakeholders for in-Hospital Management System}
 \subsection{Patients and their families:}They are the primary users of the system and have a direct interest in its functionality and reliability.
 \subsection{Hospital administrators:} They are responsible for managing the hospital's resources, including the management system, and are interested in its efficiency, effectiveness, and cost-effectiveness.
 \subsection{Clinical staff:} Doctors, nurses, and other clinical staff members use the system to manage patient information, schedules, and treatments, and are concerned with its accuracy and ease of use.
 \subsection{IT staff:} They are responsible for the installation, maintenance, and support of the system, and are interested in its technical feasibility and scalability.
 \subsection{Insurance providers:} They have an interest in the information recorded in the system, as it is used to determine patient coverage and payment for services.
 \subsection{Regulatory agencies:} They monitor the quality of healthcare services and have an interest in the accuracy and completeness of patient information recorded in the system.
 \subsection{Finance and accounting departments:} They are concerned with the financial aspects of the hospital, including budgeting, billing, and revenue management. The In-Hospital Management System plays a critical role in these processes and they have an interest in its financial reporting capabilities.

 \section{Possible conflicts between stakeholders}
\subsection{Patients and hospital administrators:} Patients may prioritize convenience and accessibility of healthcare services, while administrators may prioritize cost-effectiveness and resource utilization. For example, patients may prefer to have more testing or treatment options available, while administrators may seek to limit the number of tests or treatments to control costs.
\subsection{Clinical staff and IT staff:} Clinical staff may prioritize the ease of use and reliability of the system, while IT staff may prioritize security and scalability. For example, clinical staff may request more user-friendly interface, while IT staff may focus on implementing stronger security measures.
\subsection{Insurance providers and hospital administrators:} Insurance providers may prioritize cost control and cost sharing, while administrators may prioritize providing the best possible healthcare services to patients. For example, insurance providers may seek to limit the number of tests or treatments covered by insurance, while administrators may seek to provide more comprehensive care to patients.
\subsection{Regulatory agencies and hospital administrators:} Regulatory agencies may prioritize patient safety and quality of care, while administrators may prioritize cost-effectiveness and resource utilization. For example, regulatory agencies may require more strict reporting and documentation standards, while administrators may seek to streamline processes to reduce costs.
\subsection{Clinical staff and supply chain management:} Clinical staff may prioritize the availability of necessary medical supplies and equipment, while supply chain management may prioritize cost control and resource utilization. For example, clinical staff may request additional equipment or supplies to improve patient care, while supply chain management may seek to limit the number of items purchased to control costs.


% add a new page
\newpage
Hi there world!  Here is an example of a note\footnote{Here is a reference 
to Figure \ref{Figure::manAgile} and an indexed keyword\index{keyword}.}
\input{manHomeworkTwo.tex}